To start I would like to extend my deepest gratitude to my advisor, Prof. Kenneth S. Burch. Through many difficult assignments and tasks (some that I was convinced were impossible before trying) I have grown quite a bit since my first days in your lab building a transfer stage. Thank you for helping me become a better scientist, writer, and communicator. But more so thank you for being a mentor. \par
I would also like to thank the professors who graciously served on my dissertation committee: Professor Qiong Ma, Professor Brian Zhou, and Professor Ying Ran. I have learned quite a lot from all of you, your works, and your physics talks. I continue to be inspired by the science produced from your groups everyday. Thank you for being a role model.\par
I am extremely grateful to have had lab-mates as skilled and fun as those in LASE. The constant conversations ongoing in the lab have greatly extended my understanding of physics, chemistry, and even biology. I continue to be flabbergasted by the results produced out of the cleanroom-in-a-glovebox and I know I leave it in good hands. I would like to extend a particular thank you to a previous LASE member, Gavin Osterhoudt, for many late nights and weekends spent debating physics, MatLab, LabView, pizza, beer, and the danger levels posed by each family of animal. Thank you for the laughs!\par
In addition, I am also thankful to all of my wonderful collaborators. Your projects and papers have really made the glovebox shine in a way that would be simply impossible without you. \par
I would like to extend a thank you to the whole physics graduate student body at Boston College for making the building positive and fun. I would like to extend a special thanks to Matthew Gochan for making sure that I keep my mind and body in healthy shape. \par
I extend my thanks to the administrative staff of the Boston College physics department, Scott Bortolotto, Nancy Chevry, Jane Carter, and (formerly) S\'{i}le N\'{i} Scanl\'{a}in. The department simply would not run without you.\par
Apart from the scientific community, I want to thank my family for helping me through all the trials and tribulations of graduate school. The video and phone calls ensured that I was never too far from home.\par
I would like to thank all of my friends who have been so supportive over the last few years: Kyle, Lucas, Phil, Garrett, Glenna, Rutger, Fresca, Pippin, Gizmo, Naga, Rosa, and Lexington.\par
Lastly, I of course must thank my beautiful wife, Amanda. I could not have done this without you. 